Dependent Types for Safe and Secure Web Programming

### 2014-02-03 paper/conclusion.tex
Tiny changes

Ensuring conformance to resource usage protocols has been attempted using the notion of \emph{typestate} in object-oriented languages \cite{deline:typestates}. Our approach differs in that we make no changes to the type system in order to implement this functionality: we check resource usage protocol conformance purely within \idris{}.
Additionally, our handler-based approach facilitates greater control over side effects.

>>>>

Ensuring conformance to resource usage protocols has been attempted using the
notion of \emph{typestate} in object-oriented languages
\cite{deline:typestates}. Our approach differs in that we make no changes to
the type system in order to implement this functionality; we check resource
usage protocol conformance directly within \idris{}.  Additionally, our
handler-based approach gives greater control over side effects.
